The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-07-13 paper/paper.tex
velocities

We include two additional Milky Way simulations with similar $z = 0$ properties, which have evolutionary histories that fall in between the extremes of the two described above.  The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
\msun$.%, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.  
The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10}
\msun$.%, %and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.  
These galaxies are also described \citet{Munshi13,Bellovary14}.

>>>>

We include two additional Milky Way simulations with similar $z = 0$ properties, which have evolutionary histories that fall in between the extremes of the two described above.  The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
\msun$, and maximum circular velocity $v_{\rm circ} = 250$ km s$^{-1}$.  The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = 248$ km s$^{-1}$.  These galaxies are also described \citet{Munshi13,Bellovary14}.
